Economic Comparison of Supply Chains for Biochemical and Thermochemical Plants
============================================================

## Feedstock Location and Availability

To provide a generalized context in which the thermochemical and biochemical processing of corn stover may be compared, a square region around a centralized plant is hypothesized.  A square region, as opposed to a circular region, is selected due to the relative ease in which it's dimensions may be fit to county level data (counties are often rectangular in shape).  However, since transportation costs play a role in plant economics, only the farms located within a given distance from the plant will ultimately be considered.

Likewise, farms which have low stover production are also not considered.  Given the high density of corn production in the areas in which biorefineries are locating, low producing farms in the region of consideration will be skipped over in favor of higher producing farms.

To demonstrate this generalization, the dimensions of the square region are tuned to the total area of north central Iowa as defined in Tyndall et al. (2011), an area of 17,963 square miles.  This selection was made due to the area's high corn production and Corn Suitability Rating (CSR), an index which rates each type of soil based on its potential row crop productivity (see figure 1).  /NOTE: modify figure in research bookmarks folder to outline NC region/   Tyndall's survey results also indicate that the farmers in this region are more willing to market their stover than other regions.

**Farms with randomly generated locations within considered area**

```{r}
rm(list=ls())
##Nomenclature##
#n: number of operations
#A: considered area
#r: radius of area
#a: acres harvested per operation
#theta: Bernoulli distribution parameter

#Assumptions
n=15872 #tuned to the number of operations in North Central Iowa in 2012 according to NASS
A=17963 #tuned to area of North Central Iowa as defined by Tyndall
theta=0.23 #parameter for Bernoulli distribution

#Implied variables
r=sqrt(A)/2

# Randomly generating farms
farms<-matrix(data=NA,nrow=n,4)
colnames(farms)<-c("ID","XCoord","YCoord","Distance")

for(i in 1:n){
  farms[i,1]<-i
  farms[i,2]<-runif(1,-r,r)
  farms[i,3]<-runif(1,-r,r)
}

farms<-as.data.frame(farms)
farms$Distance<-sqrt(farms$XCoord^2+farms$YCoord^2)
```

**Method of Moments estimation of the distribution of Iowa yields**

Stover production can be estimated through use of a harvest index (weight of grain as a proportion of total crop weight) which relates the production value to the grain yield.  Since yields have spatial variation, so too will stover production.  To capture this variation, a yield distribution is needed.  Here, we assume that yields,y,follow a transformed beta distribution and is modelled through the use of $\frac{x-y_{min}}{y_{max}-y_{min}}$ where $x \sim beta(\alpha,\beta)$.  The parameters and support of this distribution follow from a method of moments approach using 2004-2013 yield data for the state of Iowa.

```{r Calculating North Central Iowa yield distribution,fig.width=7,fig.height=6}
#reading in the data
c<-"/Users/goodrich/Desktop/R Projects/Supply.Chain.Development/Iowa_corn_data_2.csv"
iowa.data<-read.table(file=c, header=TRUE,sep=",") 

#extracting yield data from 2004-2013
iowa.yield<-subset(iowa.data,Data.Item=="CORN, GRAIN - YIELD, MEASURED IN BU / ACRE")
iowa.yield<-subset(iowa.yield,Year>2004)
iowa.yield<-subset(iowa.yield,select=c(Year,County, Value))

#converting values to numeric
iowa.yield$Value<-as.numeric(as.character(iowa.yield$Value))

#calculating the support of yield variable
l<-min(iowa.yield$Value)
u<-max(iowa.yield$Value)

#transform data to standard beta distribution
iowa.yield$trans<-(iowa.yield$Value-l)/(u-l)

#method of moments estimation
mu<-mean(iowa.yield$trans)
s2<-var(iowa.yield$trans)
beta<-mu*(1-mu)^2/s2 - (1-mu)
alpha<-beta*mu/(1-mu)

hist(iowa.yield$trans,breaks=16,main="Histogram of Transformed Yield Values",freq=FALSE,xlab="Yield")
curve(dbeta(x,alpha,beta),add=TRUE,col="blue",lwd=3)
```

**Corn Stover Production**

Corn stover production then follows from a simplified version of the equation found in Graham et al. (2007): 

EQUATION 1:
Stover (kg per acre per year) = yield (bu corn per acre per year) 
                                * avg dry grain mass of a bushel of corn (kg corn per bu) 
                                * (1-dry weight harvest index) / dry weight harvest index

/Note:  This is a common assumption but R.L. Hoskinson et al. (2007) suggests that a better estimation technique uses the collected stover harvest index rather than the dry weight harvest index since mechanically speaking, it is impossible to collect the entire plant.  They report values of 0.60 and 0.66 for low (10 cm above soil) and normal (40 cm above soil) cutting techniques./

```{r yield generation and stover production calculations}
#Stover production per acre
stover.acre=function(yield,dgm,HI){
  yield*dgm*HI/(1-HI)
}

#Assumptions
dgm<-21.5 #kg/bu from Wilcke and Wyatt (2002)
HI<-0.5 #ratio of grain mass to total plant mass from Gupta (1979), DuPont discussion

#Generating Yields
farms$AvgYield<-0
for(i in 1:nrow(farms)){
  farms[i,5]<-l+(u-l)*rbeta(1,alpha,beta)}

#Calculating average stover production
farms$AvgStover<-0
for(i in 1:nrow(farms)){
  farms[i,6]<-stover.acre(farms[i,5],dgm,HI)
}
```

Assume that biorefinery will only consider farms with an average stover production of greater than 3 tons per acre (2721.555 kg).

```{r}
#Assumptions
stover.requirement<-2721.55 #kg per acre required for consideration

# Selecting only farms within given radius around the centralized plant
farms.considered<-subset(farms,Distance<r)

# Partitioning out only farms which reach the stover production requirement
farms.considered<-subset(farms.considered,farms.considered$AvgStover>stover.requirement)

# Partitioning out the farms which have agreed to provide their stover
farms.considered$Participate<-0
for(i in 1:nrow(farms.considered)){
  farms.considered[i,7]<-rbinom(1,1,theta)
}
part.farms<-subset(farms.considered,Participate==1)
```

**Depiction of considered area and participating farms**

The number of farms generated are set to match the number of corn operations in North Central Iowa in 2012, 15,872.  However, of these 15,872 corn operations, only a certain proportion of those in consideration will agree to provide their stover to the plant.  Due to the uncertainty of how much stover can be removed from the field without negatively impacting yields and long-term soil productivity, farmers have varying levels of comfort with allowing a biorefinery to harvest their stover.  From the standpoint of the biorefinery, whether a farmer will agree to participate is uncertain.  To capture this uncertainty, a farmer's willingness to participate is assumed to follow a Bernoulli($\theta$) distribution with $\theta$ tuned to 0.23 to reflect the results of Tyndall's survey paper.

```{r farm locations}
require(ggplot2)

##Partitioning out non-participating farms##
nonpart.farms<-subset(farms.considered,Participate==0)

##Partitioning out farms not considered
nonconsidered.farms<-subset(farms,Distance>r|AvgStover<stover.requirement)

##Creating array for biorefinery location##
refine.locations<-matrix(data=NA,nrow=1,3)
colnames(refine.locations)<-c("Site","XCoord","YCoord")
refine.locations<-as.data.frame(refine.locations)
refine.locations[1,1]<-"Central Facility"
refine.locations[1,2]<-0
refine.locations[1,3]<-0

##Drawing the circle##
circleFun <- function(center = c(0,0),diameter = 1, npoints = 10000){
    rr = diameter / 2
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + rr * cos(tt)
    yy <- center[2] + rr * sin(tt)
    return(data.frame(x = xx, y = yy))
}

circle <- circleFun(c(0,0),2*r,npoints = n)
#geom_path will do open circles, geom_polygon will do filled circles
ggplot(circle,aes(x,y)) + geom_path() + geom_point(data=nonpart.farms,x=nonpart.farms$XCoord,y=nonpart.farms$YCoord) + geom_point(data=part.farms,x=part.farms$XCoord,y=part.farms$YCoord,col="red")+ geom_point(data=nonconsidered.farms,x=nonconsidered.farms$XCoord,y=nonconsidered.farms$YCoord,col="gray")+ geom_point(data=refine.locations,x=refine.locations$XCoord,y=refine.locations$YCoord,col="blue",size=8)+ ggtitle("Farm Locations") + theme(plot.title = element_text(lineheight=.8, face="bold"))+xlab("Miles (West to East)")+ylab("Miles (North to South)")
```

**Acres harvested distribution**

In addition to not knowing which farms will choose to participate, the biorefinery also does not know how large the participating farm operations will be.  To account for this uncertainty, acres harvested are assumed to follow a $lognorm(\mu,\sigma)$ distribution.  The parameters of this distribution are found by minimizing the sum of squared differences between the proportion of operations in each of the six categories in which NASS provides in its 2012 survey data for the state of Iowa and the proportion in the fit distribution, subject to the constraint that the mean acreage equals the average acreage in the data.

```{r Acres harvested data}
o<-"/Users/goodrich/Desktop/R Projects/Supply.Chain.Development/NCentralOperations.csv"
operations.data<-read.table(file=o, header=TRUE,sep=",")

require(plyr)
op<-function(data) {with(data,sum(Value))}
op.dist<-ddply(operations.data, .variables="Domain.Category", .fun=op)

op.dist$ID<-c(6,1,3,2,4,5)

#ordering according to ID
op.dist<-op.dist[order(op.dist[,3]),]
```

SOMETHING WRONG WITH THIS.  HOW DO I USE DATA?
```{r Acres harvested sampler}
#Generating categorical data
op.dist.data<-as.data.frame(c(rep(op.dist[1,3],op.dist[1,2]),rep(op.dist[2,3],op.dist[2,2]),rep(op.dist[3,3],op.dist[3,2]),rep(op.dist[4,3],op.dist[4,2]),rep(op.dist[5,3],op.dist[5,2]),rep(op.dist[6,3],op.dist[6,2])))
colnames(op.dist.data)<-"Category"

require(rjags)
model="model{
    category[1:6]~dmulti(p[1:6],N)
    p[1]<-plnorm(25,log(mu),log(sigma2))
    p[2]<-plnorm(100,log(mu),log(sigma2))-plnorm(25,log(mu),log(sigma2))
    p[3]<-plnorm(250,log(mu),log(sigma2))-plnorm(100,log(mu),log(sigma2))
    p[4]<-plnorm(500,log(mu),log(sigma2))-plnorm(250,log(mu),log(sigma2))
    p[5]<-plnorm(1000,log(mu),log(sigma2))-plnorm(500,log(mu),log(sigma2))
    p[6]<-1-plnorm(1000,log(mu),log(sigma2))

    mu~dnorm(155.8869,.01)
    sigma2~dunif(log(3.328357),log(3.528357))
}
"
dat=list(N=5776)
m=jags.model(textConnection(model),dat,quiet=TRUE)
results=coda.samples(m, c("mu","sigma2"), 1000)
plot(results,trace=TRUE)

```

**Showing fit of lognormal distribution**
```{r Finding prior values for lognormal prior parameters}
#--setting up matrix for comparison of data and model--#
total_operations<-sum(op.dist$V1)

perc<-function(data) {with(data,V1/total_operations)}

model_check<-matrix(data=NA,nrow=6,5)
colnames(model_check)<-c("ID","Farm_Size","Data_Percentile","Model_Percentile","Squared_Diff")
data_perc<-ddply(op.dist,.variables="Domain.Category", .fun=perc)
model_check[,2]<-as.character(data_perc$Domain.Category)
model_check[,3]<-round(data_perc[,2],4)

#renaming category variables
model_check[1,2]<-"1000 or more acres"
model_check[2,2]<-"1 to 24.9 acres"
model_check[3,2]<-"100 to 249 acres"
model_check[4,2]<-"25 to 99.9 acres"
model_check[5,2]<-"250 to 499 acres"
model_check[6,2]<-"500 to 999 acres"

#setting ID variables
model_check[1,1]<-6
model_check[2,1]<-1
model_check[3,1]<-3
model_check[4,1]<-2
model_check[5,1]<-4
model_check[6,1]<-5

#ordering according to ID
model_check<-model_check[order(model_check[,1]),]

#--setting the parameters of the lognormal function--#
#Excel solver output
muA=178.207456
sigmaA=3.144599859

#checking the fit of the parameters
acres<-rlnorm(100000,meanlog=log(muA),sdlog=log(sigmaA)) 
model_check[1,4]<-round(plnorm(25,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE),4)
model_check[2,4]<-round(plnorm(100,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE)
      -plnorm(25,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE),4)
model_check[3,4]<-round(plnorm(250,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE)
      -plnorm(100,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE),4)
model_check[4,4]<-round(plnorm(500,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE)
      -plnorm(250,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE),4)
model_check[5,4]<-round(plnorm(1000,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE)
      -plnorm(500,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=TRUE),4)
model_check[6,4]<-round(plnorm(1000,meanlog=log(muA),sdlog=log(sigmaA),lower.tail=FALSE),4)

model_check[,5]<-round((as.numeric(model_check[,3]) - as.numeric(model_check[,4]))^2,4)

model_check
mean(acres) #actual mean is 343.5207
```

**Stover available at the farm level**

```{r calculating stover available to biorefinery at farm level}
#Assumptions
kgperton<-907.185

#Calculating collectible stover per corn operation
part.farms$AcresHarvested<-0
part.farms$Stover<-0

for(i in 1:nrow(part.farms)){
  part.farms[i,8]<-rlnorm(1,meanlog=log(muA),sdlog=log(sigmaA))
}
for(i in 1:nrow(part.farms)){
  part.farms[i,9]<-part.farms[i,6]*part.farms[i,8]
}

#Ordering by distance from plant
part.farms<-part.farms[with(part.farms, order(Distance)),]

#Calculating cumulative stover as a function of distance
part.farms$CumulativeStover<-part.farms[1,9]
for(i in 2:nrow(part.farms)){
  part.farms[i,10]<-part.farms[i,9]+part.farms[i-1,10]}
```

**Depiction of cumulative stover as a function of distance**

```{r Stover as a function of distance}
plot(part.farms$Distance,part.farms$CumulativeStover/(kgperton*1000),xlab="Distance (miles)",ylab="Collectible Stover (thousand tons)",main="Collectible Stover as a Function of Distance")
```

## Stover Harvesting, Baling, and Bale Collection

The costs of harvesting the stover, baling and bale collection are common to both types of biorefinery.  Assume a 30 day window with 10.5 hrs/day of sunlight to work with to harvest and stack bales on the edge of the field.  This is based on Darr's work and amounts to 315 hours of work per year.  Allow moisture content to vary, Petrolia assumes a lognormal distribution with mean 16 and standard deviation 11 truncated at 80%.

**Stover Collection**

Case 1: the biorefinery sets up contracts to go collect the stover themselves and uses the following process.

Step 1: 20' windrower/shredder shreds stalks and discharges material into windrow.  This type of machine is selected because shredders have less opportunity to contact the ground and hence bales will have a lower level of soil contamination than with a raking technique.  The cost of this machine goes for around $30,000 and has a recommended speed between 3 and 7 miles per hour.  At 7 miles per hour without accounting for any turns this amounts to around 16.97 acres per hour.  I assume a slightly lower estimated productivity of 15 acres per hour for 315 hours and a four year expected ownership. It is assumed to be pulled by a 60 horsepower tractor purchased for list price of $47,000 with assumed 15 years of ownership (cite: build your own John Deere).

William Edwards Machinery Cost Calculator estimates:

Ownership costs:
TRACTOR
Capital recovery (interest--assuming 5.50% and depreciation): $4120/yr; $0.87/acre
Taxes, insurance and housing: $298/yr; $0.06/acre
WINDROWER/SHREDDER
Capital recovery (interest--assuming 5.50% and depreciation): $6451/yr; $1.37/acre
Taxes, insurance and housing: $216/yr; $0.05/acre

Operating costs:
TRACTOR
Repair costs: $490/yr; $0.10/acre
Fuel and lubrication costs (assuming $3.50/gal): $3347/yr; $0.71/acre
Labor costs (assuming $14/hr): $4851/yr; $1.03/acre
WINDROWER/SHREDDER
Repair costs: $1954/yr; $0.41/acre

Step 2: Large rectangular baler pulled by 269 horsepower tractor bales windrows held together by twine.  Dimensions are 3x4x8.  Tractor ownership life assumed to be 15 years with list price of $309,000 (cite: Build Your Own John Deere).  Large rectangular baler cost assumed to be $120,000 with expected ownership period of 6 years.  Assumed to be able to run 1.5 times faster than the shredder/windrower operation at speed of 22.5 acres per hour.

William Edwards Machinery Cost Calculator estimates:

Ownership costs:
TRACTOR
Capital recovery (interest--assuming 5.50% and depreciation): $2758/yr; $0.39/acre
Taxes, insurance and housing: $190/yr; $0.03/acre
BALER
Capital recovery (interest--assuming 5.50% and depreciation): $22298/yr; $3.15/acre
Taxes, insurance and housing: $808/yr; $0.11/acre

Operating costs:
TRACTOR
Repair costs: $322/yr; $0.05/acre
Fuel and lubrication costs (assuming $3.50/gal): $15007/yr; $2.12/acre
Labor costs (assuming $14/hr): $4851/yr; $0.68/acre
BALER
Repair costs: $6290/yr; $0.89/acre

Step 3: Bale picker moves bales to field edge.

NEED TO CONSIDER TRANSPORT COSTS OF MOVING BETWEEN FIELDS.

NOTE: in Darr it says that a minimum of 250 horsepower is recommended for corn stover baling in the midwest.

COLLECTION DYNAMICS

```{r Collection assumptions}
#Assumptions (place holders)
travelspeed.windrow<-30
travelspeed.baler<-30
travelspeed.wagon<-30
tort<-1.2
workspeed.windrow<-7
workspeed.baler<-10
workspeed.wagon<-10

#sq ft in an acre
acre.sqft<-43560
acre.length<-sqrt(acre.sqft)
acre.trips<-acre.length/20
acre.distance<-acre.length*acre.trips

#Harvestable farms only graphic
ggplot(circle,aes(x,y)) + geom_path() + geom_point(data=part.farms,x=part.farms$XCoord,y=part.farms$YCoord,col="red") + geom_point(data=refine.locations,x=refine.locations$XCoord,y=refine.locations$YCoord,col="blue",size=8)+ ggtitle("Farm Locations") + theme(plot.title = element_text(lineheight=.8, face="bold"))+xlab("Miles (West to East)")+ylab("Miles (North to South)")

#Starting dataframe for farms that still have not harvested grain
notready.farms<-subset(part.farms,select=c("ID","XCoord","YCoord","Distance","AvgYield","AvgStover","AcresHarvested","Stover"))

#Renumbering of farms that still haven't harvested grain
for(i in 1:nrow(notready.farms)){
  notready.farms[i,1]<-i
}

#Introduction of dummy variable for whether or not farms have harvested grain
notready.farms$ready<-0

#Number of farms that will ultimately be harvested for stover
total.farms<-nrow(notready.farms)

#Starting dataframe for farms that have finished harvesting grain
ready.farms<-subset(notready.farms,available.farms$ready==1)

#Function for calculating percentage of farms that have harvested grain
harvest.percent=function(day){
  1-exp(-0.00000598018*day^3.36817)
}
```

```{r August 16-September 15}
for(j in 1:31){
day<-j
ready<-round(runif(round((harvest.percent(day)-harvest.percent(day-1))*total.farms),min=1,max=nrow(notready.farms)))

for(i in 1:nrow(notready.farms)){
  if(notready.farms[i,1] %in% ready){notready.farms[i,9]<-1}
}

justready.farms<-subset(notready.farms,notready.farms$ready==1)

ready.farms<-rbind(ready.farms,justready.farms)

notready.farms<-subset(notready.farms,notready.farms$ready==0)
for(i in 1:nrow(notready.farms)){
  notready.farms[i,1]<-i
}

}
ggplot(circle,aes(x,y)) + geom_path() + geom_point(data=notready.farms,x=notready.farms$XCoord,y=notready.farms$YCoord,col="red") + geom_point(data=ready.farms,x=ready.farms$XCoord,y=ready.farms$YCoord,col="green")+geom_point(data=refine.locations,x=refine.locations$XCoord,y=refine.locations$YCoord,col="blue",size=8)+ ggtitle("Farm Locations") + theme(plot.title = element_text(lineheight=.8, face="bold"))+xlab("Miles (West to East)")+ylab("Miles (North to South)")
```

```{r September 16}
day<-32

#ordering ready farms by distance from plant
ready.farms<-ready.farms[with(ready.farms, order(Distance)),]

#create vector to track the time it takes to windrow each farm
ready.farms$WindrowSiteTime<-0

#calculating the time it takes to windrow each farm
for(i in 1:nrow(ready.farms)){
  ready.farms[i,10]<-ready.farms[i,7]*acre.distance/(workspeed.windrow*5280)
}

#calculating cumulative work time (hours) to windrow
ready.farms$CumulativeWindrowTime<-ready.farms[1,10]
for(i in 2:nrow(ready.farms)){
  ready.farms[i,11]<-ready.farms[i,10]+ready.farms[i-1,11]
}

plot(x=ready.farms$Distance,y=ready.farms$CumulativeWindrowTime)

#Travel time to first stop
min(ready.farms$Distance)*tort/travelspeed.windrow
```


ready<-round(runif(round((harvest.percent(day)-harvest.percent(day-1))*total.farms),min=1,max=nrow(notready.farms)))

for(i in 1:nrow(notready.farms)){
  if(notready.farms[i,1] %in% ready){notready.farms[i,9]<-1}
}

justready.farms<-subset(notready.farms,notready.farms$ready==1)

ready.farms<-rbind(ready.farms,justready.farms)

notready.farms<-subset(notready.farms,notready.farms$ready==0)
for(i in 1:nrow(notready.farms)){
  notready.farms[i,1]<-i
}

ggplot(circle,aes(x,y)) + geom_path() + geom_point(data=notready.farms,x=notready.farms$XCoord,y=notready.farms$YCoord,col="red") + geom_point(data=ready.farms,x=ready.farms$XCoord,y=ready.farms$YCoord,col="green")+geom_point(data=refine.locations,x=refine.locations$XCoord,y=refine.locations$YCoord,col="blue",size=8)+ ggtitle("Farm Locations") + theme(plot.title = element_text(lineheight=.8, face="bold"))+xlab("Miles (West to East)")+ylab("Miles (North to South)")
```

```{r Field Edge costs}
#Notes
#Darr p.18--at 20% moisture level, dry bale weight of 1110 lb optimizes transportation efficiency of 53 ft trailer.
#Darr calculates 28.87 $/ton for multi-pass system to stack square-baled stover at field edge

#Assumptions
cost.windrow<-9.11/907.185 #dollars per kg stover to create windrow
cost.bale<-12.93/907.185 #dollars per kg stover to bale windrows
cost.edge<-6.83/907.185 #dollars per kg stover to move bales to field edge
#cost.nutrients<-9.84/907.185 #dollars per kg stover to replace nutrients (from DuPont quote)
efficiency<-0.38

#Implied assumption
#bale.weight<-bale.weight.lbs*0.453592 #bale dry weight in kg

#Calculations
#part.farms$Bales<-part.farms$StoverAvailable/bale.weight
part.farms$FieldEdgeCost<-(cost.windrow+cost.bale+cost.edge)*part.farms$Stover*efficiency
```

```{r Field Edge Costs}
hist(part.farms$FieldEdgeCost,breaks=100,xlab="Field Edge Cost (thousand $)",main="Field Edge Cost Distribution")
```

**Bale Moisture Content**

```{r Bale moisture content}
part.farms$bales
```

```{r Cost assumptions by Petrolia(2008)}
#97 kW MFWD Tractor: $79,200 initial cost.
#45 kW Tractor: $22,680 initial cost.
#Stalk Shredder 6m: $17,300 initial cost.
#JD 705 Twin Rake: $11,890 initial cost.
#Hesston 4790 Rectangular Baler: $73,880 initial cost.
#Inland 4000 Bale Mover: $28,620 initial cost.
#Deere 3220 Telehandler w/baler attachment: $68,890 initial cost.
```

```{r Time assumptions by Darr}
eff.windrow<-13*kgperton #dry kg per hour
eff.baler<-20*kgperton #dry kg per hour
eff.mover<-25*kgperton #dry kg per hour
```



## Items to come back to

**Biochemical Conversion**

```{r Biochemical Plant}
bc.conversion.ton<-70 #gallons of ethanol per ton of stover
bc.conversion<-bc.conversion.ton/907.185 #gallons of ethanol per kg of stover

part.farms$CumulativeEtoh<-part.farms$CumulativeStover*bc.conversion
```
**Energy Contents**

```{r}
#Energy Content Assumptions
e.stover<-63.5 #MJ/kg from Luo et al. (2009)
e.etoh.liter<-21.2 #MJ/L, energy content of ethanol from http://en.wikipedia.org/wiki/Ethanol
e.gas.liter<-34.8 #MJ/L, energy content of gasoline from http://en.wikipedia.org/wiki/Ethanol
e.biooil<-16.5 #MJ/kg, from Oasmaa A, Peacocke C.  A guide to physical property characterisation of biomass derived fast pyrolysis liquids.  VTT publication 450.  Technical Research Centre of Finland (VTT); 2001.  ISBN951-38-5878-2.

#Conversion
gal.per.liter<-0.26417205235815 #http://www.thecalculatorsite.com/conversions/liquidvolume/liters-to-gallons-(us).php

#Implied assumptions
e.etoh<-e.etoh.liter/gal.per.liter #MJ/gal, energy content of ethanol
e.gas<-e.gas.liter/gal.per.liter #MJ/gal, energy content of gasoline

#Density Assumptions
d.biooil<-1.207 #kg/L from potentially unreliable internet source DOUBLE CHECK

#Process conversion assumptions
tc.biooil<-.65 #wt% basis of feedstock --assumption used in Zhang et al. (2013).
```
