Feedstock Delivery Costs
========================================================

This document explores the feedstock costs of a biorefinery which converts corn stover to transportation fuels.  I begin with a setup in which the corn stover is harvested, baled, stacked at the edge of the field, then transported to the biorefinery.  I.e., satellite storage locations are not yet considered.  These costs are broken down into the following categories:

1. Harvesting
2. Baling
3. Transportation to field edge stack
4. Storage
5. Transportation to biorefinery

## Harvesting and Baling Costs #
### Multi-pass System #

There are several types of machinery that can be used to harvest corn stover.

Option 1: combine windrow
- spreaders on the back of a combine are disengaged to allow material other than grain to drop directly behind the combine at the time of grain harvest
- produces a windrow with approximately 0.75 ton/acre of material

Option 2: bar or wheel rake
- use rotating parallel bars/wheels with mounted teeth to sweep corn stover into a center windrow
- producees a windrow between 1.25-2 tons/acre of material

Option 3: windrowing stalk choppers
- use a series of rotating knives to chop or shred corn stalks.  Commonly used in the corn belt to help break down stalk material, particularly in continuous corn production.
- because the stalk choppers have less opportunity to engage the ground, the soil contamination and ash level of corn stover produced with a stalk chopper is generally less than with the bar or wheel rakes.

NOTE: Option 3 is the best for a cellulosic ethanol plant due to the decreased soil contamination and ash level.  I am not sure of how ash and soil levels impact pyrolysis.  This opens the door for options 1 and 2.

Darr has assumed windrow stalk choppers used at a production rate of 13 dry tons per hour.  The summary of production costs include:

Tractor: $25/hr.  $1.923077/ton <br />
Labor: $14/hr.  $1.076923/ton <br />
Fuel: $32.20/hr.  $2.476923/ton.  This follows from assumptions of 8 gal/hr, $3.50/gal, and 15% lubrication cost. <br />
Windrower: $27.50/hr. $2.115385/ton.  This follows from assumptions of 30 harvest days/yr, $30,000 initial cost, 4 year life. <br />
Overhead: $1.52/ton.  Follows from 20% overhead cost assumption. <br />

Example of stalk chopper: http://www.wisfarmer.com/leadstories/175612681.html

```{r}
#Inputs
harvest_days<-30 #days to harvest between grain harvest and worsening weather
harvest_hr_day<-10.5 #average hours per day in which to harvest
rate<-13 #production of dry tons per hour
price_gasoline <-3.50 #dollars per gallon for gasoline
labor_hourly<-14 #hourly charge for labor --presumably 1 employee

tractor_hourly<-25 #hourly charge of running the tractor --rental rate
harvest_fuel_hourly<-8 #gallons consumed per hour
lubrication<-0.15 #percent cost for lubricating the equipment

windrower_init<-30000 #initial cost of purchasing the windrower
windrower_life<-4 #assumed life in years of the windrower

overhead<-0.2 #percent overhead associated with management costs

#Outputs (per ton)
cost_harvest_tractor<-tractor_hourly/rate
cost_harvest_labor<-labor_hourly/rate
cost_harvest_fuel<-harvest_fuel_hourly*price_gasoline*(1+lubrication)/rate
cost_harvest_windrower<-(windrower_init/(windrower_life*harvest_days*harvest_hr_day))/rate
cost_harvest_overhead<-(cost_harvest_tractor+cost_harvest_labor+cost_harvest_fuel+cost_harvest_windrower)*overhead
(total_cost_harvest<-cost_harvest_tractor+cost_harvest_labor+cost_harvest_fuel+cost_harvest_windrower+cost_harvest_overhead)
```

Darr uses similar baling cost categories as for harvesting but with the addition of string used to tie the balers.  He assumes the baler operates at 20 dry tons per hour.  The summary of production costs include:

Tractor: $45/hr.  $2.25/ton. <br />
Labor: $18/hr. $0.90/ton. <br />
Fuel: $48.30/hr. $2.42/ton.  Assumes 12 gal/hr, $3.50/gal, 15% lubrication cost. <br />
Baler: $76.60/hr. $3.83/ton.  Assumes 30 harvest days/yr.  $120,000 initial cost, 6 yr life. <br />
String: $1.38/ton. <br />
Overhead: $2.15/ton.  Assumes 20% overhead associated with management costs.  <br />

```{r}
#Inputs
tractor_bale_hourly<-45 #rental rate of tractor pulling the baler
labor_baler_hourly<-18 #hourly rate of the baling employee
rate_baler<-20 #dry tons baled per hour
baler_fuel_hourly<-12 #gallons consumed per hour by baler running at 20 dry tons per hour

baler_init<-120000 #initial cost of baler
baler_life<-6 #assumed years of life for baler

cost_bale_string<-1.38

#Outputs (per ton)
cost_bale_tractor<-tractor_bale_hourly/rate_baler
cost_bale_labor<-labor_baler_hourly/rate_baler
cost_bale_fuel<-(baler_fuel_hourly*price_gasoline*(1+lubrication))/rate_baler
cost_bale_baler<-(baler_init/(baler_life*harvest_days*harvest_hr_day))/rate_baler
cost_bale_overhead<-(cost_bale_tractor+cost_bale_labor+cost_bale_fuel+cost_bale_baler+cost_bale_string)*overhead
(total_cost_bale<-cost_bale_tractor+cost_bale_labor+cost_bale_fuel+cost_bale_baler+cost_bale_string+cost_bale_overhead)
```

### Single pass system #

Instead of going through the field twice to first create a windrow and then bale the material, stover can be harvested and baled simultaneously.  The cost summary provided by Darr is given as:

Combine: $5.83/ton.  This follows from the assumption that a custom combine in Iowa costs $35/acre with capacity of 15 acres per hour and the single pass harvesting system will reduce the productivity of the combine by 20%.  This is a loss of $105 per hour which is distributed across the 12 acre capacity following the introduction of the harvesting system.  I.e., $8.75 per acre is charged to the biomass harvest.  Assuming a harvest rate of 1.5 ton/acre, this yields the $5.83/ton cost. <br />
Fuel: $1.61/ton.  Assumes 0.4 gal/ton, $3.50/gal, and 15% lubrication cost. <br />
Baler: $53.45/hr. $2.97/ton.  Assumes 30 harvest days/year, $120,000 initial cost, 6 year life. <br />
String: $1.38/ton
Overhead: $2.36/ton.  Assumes 20% overhead cost.

```{r}
#Inputs
rate_custom_combine<-35 #per acre cost of custom combine
capacity_custom_combine<-15 #max acres per hour of custom combine
prod_reduction<-0.20 #percent productivity reduction of combine associated with addition of harvesting system for stover

singlepass_init<-120000 #initial cost of single pass harvesting system
singlepass_life<-6 #assumed years of life for single pass harvesting system
rate_singlepass<-1.5 #tons/acre rate of single pass harvesting system
rate_fuel_singlepass<-0.4 #gallons of fuel used per ton of biomass collected

#Outputs (per ton)
cost_combine_singlepass<-(rate_custom_combine*prod_reduction)/(rate_singlepass*(1-prod_reduction))
cost_fuel_singlepass<-rate_fuel_singlepass*price_gasoline*(1+lubrication)
cost_baler_singlepass<-singlepass_init/(singlepass_life*harvest_days*harvest_hr_day*rate_singlepass*(1-prod_reduction)*capacity_custom_combine)
cost_overhead_singlepass<-(cost_combine_singlepass+cost_fuel_singlepass+cost_baler_singlepass+cost_bale_string)*overhead
(total_cost_singlepass<-cost_combine_singlepass+cost_fuel_singlepass+cost_baler_singlepass+cost_bale_string+cost_overhead_singlepass)
```

## Bale Collection #

Commercial collection systems can field stack 25 dry tons of biomass per hour.  Darr assumes six bale high field edge stacks.  The cost summary is given as:

Tractor: $42/hr. $1.68/ton. --rental rate. <br />
Labor: $18/hr.  $0.72/ton. <br />
Fuel: $40.25/hr.  $1.61/ton.  From assumption of 10 gal/hr, $3.50/gal and 15% lubrication cost <br />
Wagon: $42.13/hr.  $1.69/ton.  Assumes 30 harvest days/hear, $80,000 initial cost, 6 year life. <br />
Overhead: $1.14/ton.  Assumes 20% overhead cost.  <br />

```{r}
#Inputs
tractor_stack_hourly<-42 #hourly rental rate of tractor used to move bales to stack
rate_stack<-25 #dry tons field stacked per hour
labor_stack_hourly<-18 #hourly wage of stacking employee
stack_fuel_hourly<-10 #gallons consumed per hour by stacking system

stack_init<-80000 #initial cost of wagon
stack_life<-6 #assumed life of wagon

#Outputs (per ton)
cost_tractor_stack<-tractor_stack_hourly/rate_stack
cost_labor_stack<-labor_stack_hourly/rate_stack
cost_fuel_stack<-stack_fuel_hourly*price_gasoline*(1+lubrication)/rate_stack
cost_wagon_stack<-stack_init/(stack_life*harvest_days*harvest_hr_day)/rate_stack
cost_overhead_stack<-(cost_tractor_stack+cost_labor_stack+cost_fuel_stack+cost_wagon_stack)*overhead
(total_cost_stack<-cost_tractor_stack+cost_labor_stack+cost_fuel_stack+cost_wagon_stack+cost_overhead_stack)
```

## Transportation #

Darr shows that with 3 by 4 by 8 ft bales, the optimal satellite storage transportation distance is less than 8 miles.  Under these conditions the optimally configured harvest transportation team consists of three semi-trucks per field loading team.  The total cost of operation is around $9.50 per dry ton delivered to a satellite storage facility.  The cost of delivering from the satellite storage facility to the biorefinery approaches $7.00 per dry ton.

I SHOULD JUST LOOK UP THE COMMERCIAL RENTAL RATE FOR THIS PART.

## Feedstock Availability #

The amount of stover produced on a given acre can be estimated from the corn grain production on that acre.  Following from Graham et al. (2008) as well as from the talks with DuPont, the relationship can be defined as:

Stover (Mg per acre per year) = yield (bu corn per acre per year) 
                                * avg dry grain mass of a bushel of corn (kg corn per bu) 
                                * dry weight harvest index / (1 - dry weight harvest index)
                                * 1000 kg per Mg
                                
Next: find avg yield from NASS.  Assume uniformly distributed producers around the plant.  Look into the proportion that have continuous corn and assume a participation rate for these producers.  Assume a different (lower) participation rate for farmers which have a corn/soybean rotation.

Stover production per acre
```{r}
#Assumptions
yield<-165 #bu/acre
dgm<-21.5 #kg/bu (dry grain mass) --from Wilcke and Wyatt (2002)
HI<-0.5 #kg stover/kg plant --from Gupta et al. (1979)

#Stover production per acre
stover_acre<-yield*dgm*HI/(1-HI)
```

Acres per operation
```{r}
#Assumptions
farm_size<-333 #avg acreage per farm
```

## Feedstock Requirements #

Feedstock required as a function of production output follows from Wright and Brown's 2008 paper "Distributed processing of biomass to bio-oil for subesquent production of Fischer-Tropsch liquids".

The relationship between feedstock required and production output can be parameterized as:

$F*E_{stover}*\eta_{BTL}=M*E_g$

where F is the required quantity of corn stover (kg), M is the desired output (gge), $E_{stover}$ is the energy content of stover, $E_g$ is the energy content of gasoline, and $\eta_{BTL}$ is the efficiency of the biomass to liquid process.